---
title: "Eco2Urb data"
output:
  html_document:
    df_print: paged
---


```{r}
setwd("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb")
library(sf)
library(ggplot2)
library(raster)
library(tiff)
```

```{r}
list.files()

setwd("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters")
list.files()
```

```{r 11A}
tiff_11A <- read.asciigrid("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig11a.asc")
 
plot(tiff_11A)
```



```{r 11B}
tiff_11B <- read.asciigrid("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig11b.asc")
 
plot(tiff_11B)
```


```{r 11C}
tiff_11C <- read.asciigrid("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig11c.asc")
 
plot(tiff_11C)
```




```{r 13}
tiff_13 <- raster("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig13.tif")
 
plot(tiff_13)
```


```{r 14}
tiff_14 <- raster("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig14.tif")
 
plot(tiff_14)
```


```{r 15}
tiff_15 <- raster("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig15.tif")
 
plot(tiff_15)
```


```{r 16}
tiff_16 <- raster("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Fig16.tif")
 
plot(tiff_16)
```

```{r}
heat_islands <- read.asciigrid("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/heatcoolislands/heatislands3.asc")
cool_islands <- read.asciigrid("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/heatcoolislands/coolislands5.asc")

plot(heat_islands)
plot(cool_islands)
```

```{r}
flood <- raster("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/DSF2FinalRasters/Flood_CMM.tif/Flood_CMM.tif")
plot(flood)
```


```{r}

montreal_ES <- st_read("/Users/Ty/Dropbox/Dendritic connectivity/SUS2020/data/Eco2Urb/montreal-agglomeration-muni-100028-div-vf1-20201125.shp")
```

```{r}

ggplot(montreal_ES) +
      geom_sf(aes(fill = can_area), color = "white", 
              size = 0.05) 
```

```{r}
names(montreal_ES)
```


"SP_ID" [integer]     = shape ID
"nom_arr" [character] = name of area described by shape
"can_area" [number]   = ? what is can?
"muni_area" [integer] = why is this an integer?
"perc_co"   [number]  = ?
"sp"  [integer]       = number of species observed in shape area? Is this a model or data?
"rrar"  [number]     = ?
"abun"   [integer]    = abundance of something?
"trunof"  [number]   = ?
"stand_run"  [number]= something about water runoff?
"polrem"    [number]= polution remediation? 
"stand_pol"  [number]= standing polution?
"carbon" [number]    = what about carbon?
"stand_car" [number] = why is this a decimal if the unit is a car? is this number of cars that park in a shape?
"Sequestrat"[number] = sequestering rats? 
"stand_seq" [number] = standing sequestration of something. 
"Evap"   [number]    = evaporation from trees?
"stand_evap" [number]= standing evaporation? evaporation from standing vegetation? meaning seasonal?
"mtl"   [factor]     = in MTL city limits or data provided by MTL? or other?
"order"    [factor]  = ?
"cancarbon2" [number]= what is special about the 'can' designation? Are the data from canadian federal sources? 
"canrunoffa"[number]=
"canseq2" [number]  =
"canpoll" [number]   = what is poll?




